---
title: "Work with text"
author: "ditiatev"
date: "31 05 2020"
output: html_document
---

# Data

```{r}
if (!file.exists("data")) {dir.create("data")}
FileUrl <- "https://data.baltimorecity.gov/api/views/dz54-2aru/rows.csv?accessType=DOWNLOAD"
fileUrl1 <- "https://raw.githubusercontent.com/jtleek/dataanalysis/master/week2/007summarizingData/data/reviews.csv"
fileUrl2 <- "https://raw.githubusercontent.com/jtleek/dataanalysis/master/week2/007summarizingData/data/solutions.csv"
download.file(FileUrl, destfile = "./data/camera.csv")
download.file(fileUrl1, destfile = "./data/reviews.csv")
download.file(fileUrl2, destfile = "./data/solution.csv")
cameraData <- read.csv("./data/camera.csv")
reviews <- read.csv("./data/reviews.csv")
solution <- read.csv("./data/solution.csv")
```


# LowerCase
- tolower()

### tolower()
- make all character in lowercase
```{r}
names(cameraData)
```

```{r}
tolower(names(cameraData))
```

# Spliting
- strsplit()

### strsplit()
- split string by character
```{r}
splitNames <- strsplit(names(cameraData),"\\.")
splitNames[[7]]
```


# Replacing character
- sub(), gsub()
```{r}
testName <- "this_is_a_test"
```

### sub() 
- replaced one (first) character on another
```{r}
sub("_","",testName)
```

### gsub()
- replaced one (all) character on another
```{r}
gsub("_","",testName)
```


# Finding values 
- grep(), grepl()

```{r}
head(cameraData$intersection)
```

### grep()
- finding index with text which including interesting word
```{r}
grep("Alameda", cameraData$intersection)
```

- return values
```{r}
grep("Alameda", cameraData$intersection, value = T)
```


### grepl()
- return True or False
```{r}
table(
    grepl("Alameda", cameraData$intersection)
    )
```

- we can make subset
```{r}
cameraData[grep("Alameda", cameraData$intersection),]
```

## library_STRINGR

```{r}
library(stringr)
```

### nchar()
- return numbers of strings
```{r}
nchar("Ditiatev Iurii")
```

### substr()
- return substring by position
```{r}
substr("Ditiatev Iurii",2,7)
```

### str_trim()
- delete extra spaces at begining/end of string
```{r}
str_trim("Ditiatev     ")
```




















