---
title: "Week1_lab"
author: "ditiatev"
date: "06 04 2020"
output: html_document
---

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
library(GGally)
```


```{r read data}
hw1_data <- read.csv('C:/R/0_courses/JHU_DataScience/R_Programming/Week1/hw1_data.csv')
```
```{r}
head(hw1_data,2)
```

```{r}
tail(hw1_data,2)
```
```{r}
hw1_data %>%
  slice(47)
```

```{r}
hw1_data %>%
  summary()
```

```{r}
hw1_data %>%
  filter(Ozone > 31) %>%
  filter(Temp > 90) %>%
  summary()
```

```{r}
hw1_data %>%
  filter(Month == 6) %>%
  summary()
```

```{r}
hw1_data %>%
  filter(Month == 5) %>%
  summary()
```
```{r}

```

| You can exit swirl and return to the R prompt (>) at any time by pressing the
| Esc key. If you are already at the prompt, type bye() to exit and save your
| progress. When you exit properly, you'll see a short message letting you know
| you've done so.

| When you are at the R prompt (>):
| -- Typing skip() allows you to skip the current question.
| -- Typing play() lets you experiment with R on your own; swirl will ignore
| what you do...
| -- UNTIL you type nxt() which will regain swirl's attention.
| -- Typing bye() causes swirl to exit. Your progress will be saved.
| -- Typing main() returns you to swirl's main menu.
| -- Typing info() displays these options again.

| Let's get started!
