---
title: "Apply_FinF_Debuging"
author: "ditiatev"
date: "18 05 2020"
output: html_document
---
# Apply

```{r}
a <- array(rnorm(2*3*10),c(2,3,10))
a
```

We can slice symmary of matrix. // sapply, lapply.

```{r}
apply(a, c(1,2), sum)
```


**

```{r}
mapply(rnorm, 1:5,1:5,5)
```

Get symmary by some factor.

```{r}
x <- c(rnorm(10),runif(10),rnorm(10,1))
f <- gl(3,10)
tapply(x,f,mean)
```

Split data by combinations of factors. This functin can be used with apply.

```{r}
f1 <- gl(3,10)
f2 <- gl(10,3)
split(x,list(f1,f2), drop = T)
```

# Debuging

```{r}
traceback()
options(error = recover)
```

Go into function with here environment.

```{r}
debug(lm)
```

```{r}
lm(y ~ x)
```

# Function in function

Function can even return outher functions.

```{r}
makeVector <- function(x = numeric()) {
  m <- NULL
  set <- function(y) {
    x <<- y
    m <<- NULL
  }
  get <- function() x
  setmean <- function(mean) m <<- mean
  getmean <- function() m
  list(set = set, get = get,
       setmean = setmean,
       getmean = getmean)
}

cachemean <- function(x, ...) {
  m <- x$getmean()
  if(!is.null(m)) {
    message("getting cached data")
    return(m)
  }
  data <- x$get()
  m <- mean(data, ...)
  x$setmean(m)
  m
}
```


# Practical example

Function return hospitals by rank and state.
Used tapply with custom function.
Used timing measurement.

```{r}
rankall <- function(outcome, num = "best") {
    ## Read outcome data
    data <- read.csv("C:/R/0_courses/JHU_DataScience/R_Programming/Week4/outcome-of-care-measures.csv", colClasses = "character")
    
    ## Check outcome are valid
    if (!(outcome %in% c("heart attack", "heart failure", "pneumonia"))) stop(" invalid  outcome")
    
    ## Return hospital name in that state with lowest 30-day death
    colnum <- function(outcome) {
        n <- if (outcome == "heart attack") {
            11
        } else if (outcome == "heart failure") {
            17
        } else {
            23
        }
        n
    }
    
    n <- colnum(outcome)
    data <- data[which(data[,n] != "Not Available"),]
    data[,n] <- as.numeric(data[,n])
    data <- data[order(data$State,data[,n],data[,2]),]
    
    ## rate
    rate <- function(x, num)
    if (num == "best") {
        x[1]
        #data[[1,2]]
    } else if (num == "worst") {
        #data[[nrow(data),2]]
        x[length(x)]
    } else if (num > length(x)) {
        NaN
    } else {
        x[num]
    }
   
    df1 <- tapply(data[,2], data$State, FUN = function(x) rate(x, num))
    df2 <- tapply(data[,n], data$State, FUN = function(x) rate(x, num))
    df3 <- tapply(data[,7], data$State, FUN = function(x) rate(x, num))
    df <- cbind.data.frame(hospital = df1, rank = df2, state = df3)
    df
}
```

Function execution with timing measurement.

```{r}
Rprof()
rankall("heart attack", num = 3)
Rprof(NULL)
```


```{r}
s <- summaryRprof()
s
```

Other way.

```{r}
system.time(rankall("heart attack", num = 3))
```



